Grappa: Scalable Computing on Commodity Hardware \\for Irregular Applications

### 2012-07-23 doc/asplos13/evaluation.tex
threshold discussion

\begin{figure}[htb]
\begin{center}
  \includegraphics[width=0.95\columnwidth]{figs/bfs_sweep_flushticks}
\begin{minipage}{0.95\columnwidth}
  \caption{\label{fig:bfs-sweep-flushticks} Sensitivity to aggregation delay}
\end{minipage}
\vspace{-3ex}
\end{center}
\end{figure}

@@

\subsubsection{Work stealing parameters}

\paragraph{Chunk size}

It is important to steal multiple tasks at a time to both amortize the
cost of stealing over the network and to spread out work quickly in a
large system. Figure~\ref{fig:ut_chunksize} shows performance and
stealing statistics for UTS on \checkme{30} nodes as we increase the stealing chunk size. Recall
that a thief will take a number of tasks equal to the minimum of half
the available work or the chunk size; steals fail only when the victim
has fewer than 2 available tasks. As the scheduler is allowed to
steal more work beyond 1 task, we see that performance increases up to 6x. This
shows that the heuristic of stealing the oldest task from victims is
insufficient alone when a tree-structured computation is imbalanced,
as observed in \cite{UTS}. By observing sampled state in the execution
trace, we find that a chunk size as low as 1 allows stealing to
spread the load evenly across the cluster but cores spend much time
underutilized as multiple workers wait for steal replies that
utlimately return little new work.

Performance plateaus before maximum steal amount is limited by the
size of the victim's task queue. This indicates that artificially limiting steals
to \checkme{128} tasks does not limit performance. Although a lower
chunk size limits how quickly work spreads, for sufficient chunk size,
the heuristic of stealing the oldest tasks from victims in tree-based computations allows for
stolen work to expand quickly.

%% UTS: chunk size
\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{figs/uts_chunksize.pdf}
    \end{center}
    \caption{Performance of UTS-Mem with varying maximum chunk size of
    steals, run with 30 nodes, 6 cores per node, 4000 workers,
    \checkme{6M flush ticks}}
    \label{fig:uts_chunksize}
\end{figure}

@@

Parallel overhead---in the form of context switches, task spawns, and
synchronization---can reduce the performance benefit of parallelism.
Grappa sees a benefit to limiting the amount of parallelism created by
a recursive loop decomposition. The parallel loop threshold (``parallel
granularity'') parameter tells the runtime when to stop creating new tasks and just execute iterations
sequentially. This allows us to amoritize the overhead of task
creation. In addition, assigning sequential iterations to a single
task provides the potential to exploit locality when data for adjacent iterations is
also adjacent in memory.

@@

% uts threshold
\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{figs/uts_threshold.pdf}
    \end{center}
    \caption{Performance of UTS-Mem with varying parallel loop
        threshold, run with 30 nodes, 6 cores per node, 4000 workers,
    \checkme{6M flush ticks}}
    \label{fig:uts_threshold}
\end{figure}

>>>>

\begin{figure}[htb]
\begin{center}
  \includegraphics[width=0.95\columnwidth]{figs/flushticks_sweep}
\begin{minipage}{0.95\columnwidth}
  \caption{\label{fig:bfs-sweep-flushticks} Sensitivity to aggregation delay}
\end{minipage}
\vspace{-3ex}
\end{center}
\end{figure}

@@

%\subsubsection{Work stealing parameters}
%
%\paragraph{Chunk size}
%
%It is important to steal multiple tasks at a time to both amortize the
%cost of stealing over the network and to spread out work quickly in a
%large system. Figure~\ref{fig:ut_chunksize} shows performance and
%stealing statistics for UTS on \checkme{30} nodes as we increase the stealing chunk size. Recall
%that a thief will take a number of tasks equal to the minimum of half
%the available work or the chunk size; steals fail only when the victim
%has fewer than 2 available tasks. As the scheduler is allowed to
%steal more work beyond 1 task, we see that performance increases up to 6x. This
%shows that the heuristic of stealing the oldest task from victims is
%insufficient alone when a tree-structured computation is imbalanced,
%as observed in \cite{UTS}. By observing sampled state in the execution
%trace, we find that a chunk size as low as 1 allows stealing to
%spread the load evenly across the cluster but cores spend much time
%underutilized as multiple workers wait for steal replies that
%utlimately return little new work.
%
%Performance plateaus before maximum steal amount is limited by the
%size of the victim's task queue. This indicates that artificially limiting steals
%to \checkme{128} tasks does not limit performance. Although a lower
%chunk size limits how quickly work spreads, for sufficient chunk size,
%the heuristic of stealing the oldest tasks from victims in tree-based computations allows for
%stolen work to expand quickly.

%% UTS: chunk size
%\begin{figure}[ht]
%    \begin{center}
%      \includegraphics[width=0.5\textwidth]{figs/uts_chunksize.pdf}
%    \end{center}
%    \caption{Performance of UTS-Mem with varying maximum chunk size of
%    steals, run with 30 nodes, 6 cores per node, 4000 workers,
%    \checkme{6M flush ticks}}
%    \label{fig:uts_chunksize}
%\end{figure}

@@

Parallel overhead---in the form of context switches, task spawns, and
synchronization---can reduce the performance benefit of parallelism.
Grappa sees a benefit to limiting the amount of parallelism created by
a recursive loop decomposition. The parallel loop threshold (``parallel
granularity'') parameter tells the runtime when to stop creating new tasks and just execute iterations
sequentially. This allows us to amoritize the overhead of task
creation. In addition, assigning sequential iterations to a single
task provides the potential to exploit locality when data for adjacent iterations is
also adjacent in memory. The ability to exploit this locality that
exists in the application is an important advantage. We found that in UTS and BFS, increasing the
threshold from 1 up to 8 or 16, respectively, increases performance by
more than 60\%.

@@

% uts threshold
%\begin{figure}[ht]
%    \begin{center}
%      \includegraphics[width=0.5\textwidth]{figs/uts_threshold.pdf}
%    \end{center}
%    \caption{Performance of UTS-Mem with varying parallel loop
%        threshold, run with 30 nodes, 6 cores per node, 4000 workers,
%    \checkme{6M flush ticks}}
%    \label{fig:uts_threshold}
%\end{figure}
